---
title: "Assignment 4"
author: "Jonathan Flores"
date: "February 2, 2018"
output:
  html_document: default
  word_document: default
---
## Question 1

FiveThirtyEight Data (30 points): Navigate on GitHub to
https://github.com/rudeboybert/fivethirtyeight and read README.md. It includes everything
you need.

a. Install the fivethirtyeight package.

```{r echo=TRUE, results='asis'}

## install.packages("fivethirtyeight")

```

b. In the listing of Data sets in package ‘fivethirtyeight,’ assign the eighteenth data set to an object ‘df.’


```{r echo=TRUE, results='asis'}

data(package = "fivethirtyeight")

```

Note: A large list of datasets shows, college_recent_grads is the 18th dataset. Not displaying the list as it is large


```{r echo=TRUE, results='asis'}

df <- fivethirtyeight::college_recent_grads

## Displaying the first rows of the dataset to make sure it was assigned correctly

head(df)


```


c. Use a more detailed list of the data sets to write out the URL in a comment to the
related news story.


```{r echo=TRUE, results='asis'}

## Vignette function details the dataset in much more detail. Assigning this to a variable, the variable can be used to be included in a related news story

URL <- vignette("fivethirtyeight", package = "fivethirtyeight")

```

d. Using R command(s), give the dimensions and column names of this data frame.


```{r echo=TRUE, results='asis'}

## When using knitr and kableExtra libraries, we can format the tables according to specifications. Below showing the dataset with respective column names and dimensions for a table. Also, included a hover and scroll box to better fit the table on the screen

library(knitr)
library(kableExtra)
kable(df,"html") %>%
  kable_styling(bootstrap_options = c("striped", "hover"), full_width = F, font_size = 9) %>%
  scroll_box(width = "900px", height = "600px")
  

```



## 2. Data Summary (30 points): 

Use your newly assigned data frame for Question 2.

a. Write an R command that gives you the column names of the data frame. Right after
that, write one that counts the number of columns but not rows. Hint: The number
should match one of your numbers in Question 1d for dimensions.


```{r echo=TRUE, results='asis'}

colnames(df)
length(colnames(df))

```



b. Generate a count of each unique major_category in the data frame. I recommend using libraries to help. To be clear, this should look like a matrix or data frame containing the major_category and the frequency it occurs in the dataset. Assign it to major_count.


```{r echo=TRUE, results='asis',background="black"}

library(plyr)
major_count <- count(df$major_category)
knitr::kable(major_count,"html")

```


c.  To make things easier to read, put par(las=2) before your plot to make the text perpendicular to the axis. Make a barplot of major_count. Make sure to label the title with something informative (check the vignette if you need), label the x and y axis, and make it any color other than grey. Assign the major_category labels to their respective bar. Flip the barplot horizontally so that bars extend to the right, not upward. All of these options can be done in a single pass of barplot(). Note: It’s okay if it’s wider than the preview pane

```{r echo=TRUE, results='asis'}

par(las=2)
barplot(major_count$freq,axisnames = TRUE,space = 2,main = "Frequency of Major Categories", horiz = TRUE, font_size = 5,xlab="Major Categories",ylab="Frequency",cex.names = .5, cex.axis = .5,col = "blue")


```


d. Write the fivethirtyeight data to a csv file. Make sure that it does not have row labels.

```{r echo=TRUE, results='asis'}

setwd("C:/Users/jfzjonathan/Desktop/Doing Data Science/Unit 4")
write.csv(major_count,file="Major_Count.csv",row.names = FALSE)


```

## 3. Codebook

a. Start a new repository on GitHub for your SMU MSDS homework. On your local device, make sure there is a directory for Homework at the minimum; you are welcome to add whatever you would like to this repo in addition to your requirements here.


```{r echo=TRUE, results='asis'}

## Repo was created in github, named "Homework4" as well as in local computer

```

b. Create a README.md file which explains the purpose of the repository, the topics included, the sources for the material you post, and contact information in case of questions. Remember, the one in the root directory should be general. You are welcome to make short READMEs for each assignment individually in other folders.


```{r echo=TRUE, results='asis'}

## README file has been created in the repo

```


c.In one (or more) of the nested directories, post your RMarkdown script, HTML file,
and data from ‘fivethirtyeight.’ Make sure that in your README or elsewhere that
you credit fivethirtyeight in some way.


## The response on pushing the documents to the remote repo below

C:\Users\jfzjonathan\Desktop\Doing Data Science\Unit 4\Homework4>git add .

C:\Users\jfzjonathan\Desktop\Doing Data Science\Unit 4\Homework4>git commit -a -m "Initial Commit"
On branch master
nothing to commit, working tree clean

C:\Users\jfzjonathan\Desktop\Doing Data Science\Unit 4\Homework4>git push origin master
To https://github.com/jfzjonathan/Homework4.git
 ! [rejected]        master -> master (fetch first)
error: failed to push some refs to 'https://github.com/jfzjonathan/Homework4.git'
hint: Updates were rejected because the remote contains work that you do
hint: not have locally. This is usually caused by another repository pushing
hint: to the same ref. You may want to first integrate the remote changes
hint: (e.g., 'git pull ...') before pushing again.
hint: See the 'Note about fast-forwards' in 'git push --help' for details.

C:\Users\jfzjonathan\Desktop\Doing Data Science\Unit 4\Homework4>git push --force origin master
Counting objects: 9, done.
Delta compression using up to 4 threads.
Compressing objects: 100% (7/7), done.
Writing objects: 100% (9/9), 270.87 KiB | 6.30 MiB/s, done.
Total 9 (delta 0), reused 0 (delta 0)
To https://github.com/jfzjonathan/Homework4.git
 + e659b68...36bfb85 master -> master (forced update)



d. In your RMarkdown script, please provide the link to this GitHub so the grader can see
it.

## The URL for the GitHUB is 

https://github.com/jfzjonathan/Homework4

